Examining FDR correction issue in clusterProfiler - RNA-seq example

### 2024-09-05 analysis/analyse_rnaseq2.Rmd
table of results for fdr prob

>>>>

## Table for reviewer

```{r,table}

library(reshape2)
res2a <- as.matrix(acast(res1, Var1~Var2, fun.aggregate = sum, value.var="nsig_bad"))
rownames(res2a) <- gsub("bulkrna","d",rownames(res2a))
rownames(res2a) <- gsub(".Rds"," original",rownames(res2a))

res2b <- as.matrix(acast(res1, Var1~Var2, fun.aggregate = sum, value.var="nsig_good"))
rownames(res2b) <- gsub("bulkrna","d",rownames(res2b))
rownames(res2b) <- gsub(".Rds"," corrected",rownames(res2b))

res2 <- rbind(res2a,res2b)
res2 <- res2[order(rownames(res2)),]
res2c <- rowMeans(res2)
res2 <- cbind(res2,res2c)

res2 %>%
  kbl(row.names = TRUE, caption="Effect of FDR problem correction across seven studies and nine gene set libraries") %>%
  kable_paper("hover", full_width = F)

saveRDS(res2,"fdrprob.rds")
